---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# datascience

<!-- badges: start -->
<!-- badges: end -->

The goal of the package datascience is to support the readers of the
book “Data Science und Statistik mit R” with samples, functions and tutorials
as described in the book.

The function ds.summary() automatically evaluates the main descriptive statistical figures 
for a variable and creates a histogram and box-plot for quantitative variables or a bar-chart
for qualitative variables.

## Installation

You can install the package datascience from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bheesen/datascience")
library(datascience)
```

## Tutorials

You can start the tutorials of the package with the following commands:

``` r
# R Grundlagen
ds.tutorial(name = "ds.syntax")
ds.tutorial(name = "ds.datentypen")
ds.tutorial(name = "ds.datenstrukturen")
ds.tutorial(name = "ds.operationen")
ds.tutorial(name = "ds.importexport")
ds.tutorial(name = "ds.transformation")
ds.tutorial(name = "ds.visualisierung")
ds.tutorial(name = "ds.visualisierungdynamisch")
# Statistik
ds.tutorial(name = "ds.deskriptiv")
ds.tutorial(name = "ds.verteilung")
ds.tutorial(name = "ds.visualisierungstatistik")
ds.tutorial(name = "ds.zufallsvariablen")
ds.tutorial(name = "ds.wahrscheinlichkeitsverteilung")
ds.tutorial(name = "ds.bedingtewahrscheinlichkeit")
ds.tutorial(name = "ds.induktiv")
```

## Example

This is an example using some of the functions included in the package:

```{r studierende}
library(datascience)
colnames(studierende)[c(5,10,13)] <- c("Größe","Fußball","Attraktivität")            # Spalten umbenennen
ds.summary(studierende$Größe, "Körpergröße der Studierenden","Körpergröße (in cm)")  # Quantitative Variable
ds.summary(studierende$Geburtsmonat,"Geburtsmonat der Studierenden","Geburtsmonat")  # Qualitative Variable
```

The `README.Rmd` file was used to create the `README.md` file using the function `devtools::build_readme()`.
